### 2021-03-04 treatise-context/1_introduction.tex
Criticize Bajwa et al

It also is different from Bajwa et.\ al.\ \cite [BHS10];
while they require a series of random pilot vectors and consequently the sensing stage take considerable time, we require only i.i.d.\ random sensing matrices and take just a few time frames.
Also, their constraint on \m {\ell_0} norm may not hold, and they restrict to single antenna case.

>>>>

Our work is also an improvement to Bajwa et.\ al.\ \cite [BHS10].
First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
Second, for mm waves, the channel might have a short response, requiring us to send the training signals in a short interval of time, which may not be practical.
Third, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
Fourth, generating random sequences can lead to high complexity \cite [LGL16].

### 2021-03-04 treatise-pdflatex/1_introduction.tex
Criticize Bajwa et al

It also is different from Bajwa et.\ al.\ \cite {BHS10};
while they require a series of random pilot vectors and consequently the sensing stage take considerable time, we require only i.i.d.\ random sensing matrices and take just a few time frames.
Also, their constraint on \m {\ell_0} norm may not hold, and they restrict to single antenna case.

>>>>

Our work is also an improvement to Bajwa et.\ al.\ \cite {BHS10}.
First, their method takes many time slices, but, since we consider a time independent channel matrix, a few time slices suffice.
Second, for mm waves, the channel might have a short response, requiring us to send the training signals in a short interval of time, which may not be practical.
Third, with the further constraint of hybrid beamforming, it is not clear whether their guarantee theorem for recovery is still valid.
Fourth, generating random sequences can lead to high complexity \cite {LGL16}.
